---
title: "MOA_annotation_PRISM"
author: "Maria Butjosa"

---

```{r setup}
library(dplyr)
library(tidyr)
library(ggplot2)
```


## MOAs by python

```{r MOAs python}
prism_data <- read.csv('figures/data/secondary-screen-replicate-treatment-info.csv')

# moas_prism_join %>% filter(grepl(pattern = 'strogen',moas))

python_chembls_moas <- read.csv('data_curation_annotation/intermediate_files/moas_df_python.csv') %>% 
  mutate(MOAs = gsub( pattern = '\\:\\(',replacement = '',MOAs)) %>% 
  mutate(MOAs = gsub( pattern = '\\, $',replacement = '',MOAs)) %>% 
  separate_rows(MOAs, sep = ', ') %>% distinct() %>% mutate(moas = MOAs) %>% 
  select(-MOAs)
# 
# moas_prism_join %>% filter(is.na(moas_curated)|moas_curated == '') %>% 
#   separate_rows(moa, sep = ', ') %>% distinct() %>% 
#   mutate(moas_curated = moa) %>% group_by(moas_curated) %>% count() %>% arrange(desc(n))
```

```{r}


chembl_python_moas <- left_join(read.csv('data_curation_annotation/intermediate_files/chemblids_df_python_prism.csv')%>% 
                                  select(-c(moas,`X.1`)) %>% distinct(),
                                python_chembls_moas, by = c('X0' = 'X'))

chembl_python_moas <- chembl_python_moas  %>% filter(!is.na(moas)) %>% 
  filter(!is.na(moas)) %>% filter(moas != '') %>%  mutate(source = 'chEMBL') %>% 
  mutate(name = X) %>% 
  select(name, moas, source)


prism_moas <- prism_data %>% select(name,moa) %>% separate_rows(moa, sep = ", ") %>% 
  filter(!is.na(moa))  %>% distinct() %>% mutate(moas = moa) %>% 
  mutate(source = 'PRISM') %>% select(-moa)

moas_prism_join <- rbind(chembl_python_moas,prism_moas)

moas_prism_join %>% filter(grepl('opamine|D[0-3]',moas)) %>% arrange(moas)
# moas_chembl_prism <- right_join(chembl_python_moas , prism_data %>% select(name,moa, target),
#                                by = c('X' = 'name')) %>% distinct()
# 
# moas_prism_join <-  moas_chembl_prism %>% separate_rows(MOAs, sep = ", ") %>% 
#   select(X, X0, MOAs, moa, target) %>% mutate(moas = MOAs) %>% select(-MOAs)

```
```{r}
moas_prism_join <- moas_prism_join %>% 
  mutate(moas = paste(toupper(substr(moas, 1, 1)), substr(moas, 2, nchar(moas)), sep = ""))
```

## Annotation function

```{r Annotation functions}
moas_curated <- ''
str_annotate_1 <- function(str_vector,moa_new_name){
  moas_prism_join %>%
    mutate(
      moas_matched = grepl(paste(str_vector, collapse = "|"), moas),
      moas_curated = ifelse(moas_matched , moa_new_name, moas_curated)) %>% 
    select(-c('moas_matched'))
}

```


## Cell cycle

```{r Cell cycle}
moas_prism_join <- str_annotate_1(str_vector = c('wee','PLK', 'WEE','plk'), moa_new_name = 'Wee/Plk inhibitor') 

moas_prism_join <- str_annotate_1(str_vector = c('CDK','yclin dep', 'Cyclin'), moa_new_name = 'CDK inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('CHEK','Chk','CHK'), moa_new_name = 'Chk inhibitor') 

```

### Apoptosis and p53-related pathways

```{r Apoptosis}

moas_prism_join <- str_annotate_1(str_vector = c('poptosis','Bcl','BIRC5','MCL1'), 
                                  moa_new_name = 'Apoptosis regulator inhibitor') 
```

```{r p53 pathway}
moas_prism_join <- str_annotate_1(str_vector = c('MDM2', 'mdmd2', 'p53|P53','Mdm','MDM'), moa_new_name = 'MDM2 inhibitor') 

```

### MAPK annotation

```{r MAPK chEMBL}

moas_prism_join <- str_annotate_1(str_vector = c('RAF|raf'), moa_new_name = 'RAF kinase inhibitor') 
moas_prism_join <- str_annotate_1(str_vector = c('MEK', 'mitogen-activated protein kinase kinase'), moa_new_name = 'MEK inhibitor') 
moas_prism_join <- str_annotate_1(str_vector = c('ERK'), moa_new_name = 'ERK inhibitor') 

```

There are tubulin inhibitors, disrupting agents and stabilisers. I add them all under Tublin inhibitors umbrella.

```{r Mitosis}

moas_prism_join <- str_annotate_1(str_vector = c('Aur'), moa_new_name = 'Aurora kinase inhibitor') 

moas_prism_join <- str_annotate_1(str_vector = c('ubulin'), moa_new_name = 'Tubulin inhibitor') 

moas_prism_join <-str_annotate_1(str_vector = c('ATR'), moa_new_name = 'ATR inhibitor')

```

### Hormone 
Estrogen receptor are not classified as antagonist and agonist because some are not specified and others are aslo jus modulators. 

```{r Hormone annotation}


moas_prism_join <- str_annotate_1(str_vector = c('strogen.* agonist','SERM'), moa_new_name = 'Estrogen receptor agonist') 
moas_prism_join <- str_annotate_1(str_vector = c('strogen receptor antagonist'), moa_new_name = 'Estrogen receptor antagonist') 
moas_prism_join <- str_annotate_1(str_vector = c('ndrogen'), moa_new_name = 'Androgen receptor/biosynthesis modulator')
moas_prism_join <- str_annotate_1(str_vector = c('rogesterone receptor \\bagonist\\b',
                                                 'rogesterone receptor modulator'), 
                                  moa_new_name = 'Progesterone receptor agonist/modulator')

moas_prism_join <- str_annotate_1(str_vector = c('rogesterone receptor antagonist'), 
                                  moa_new_name = 'Progesterone receptor antagonist')



```

### Chromatin regulation

```{r Polymarase and topoisomerase inhibitors}

moas_prism_join <- str_annotate_1(str_vector = c('topoisomerase'), moa_new_name = 'Topoisomerase inhibitor') 
moas_prism_join <- str_annotate_1(str_vector = c('opoisomerase IV'), moa_new_name = 'Bacterial topoisomerase inhibitor') 
moas_prism_join <- str_annotate_1(str_vector = c('^DNA poly'), moa_new_name = 'DNA polymerase inhibitor') 
moas_prism_join <- str_annotate_1(str_vector = c(' DNA poly'), moa_new_name = 'HH1 DNA polymerase inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('ADP-ribose', 'PARP'), moa_new_name = 'PARP inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('RNA polymerase'), moa_new_name = 'RNA polymerase') 

```


### PI3K/mTOR signaling

```{r PI3/Akt/mTOR kinases annotated}

moas_prism_join <- str_annotate_1(str_vector = c('mTOR|MTOR'), moa_new_name = 'mTOR inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('AKT', 'Akt', 'PKB'), moa_new_name = 'AKT inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('PI3','phosphatidylinositol'), moa_new_name = 'PI3K inhibitor') 

```

```{r Metalloproteases}
moas_prism_join <- str_annotate_1(str_vector = c('metallo'), moa_new_name = 'Matrix metalloprotease inhibitor')
```


```{r Vit D}
moas_prism_join <- str_annotate_1(str_vector = c('itamin'), moa_new_name = 'Vitamin D receptor agonist')
```


```{r Protein degradation}
moas_prism_join <- str_annotate_1(str_vector = c('proteosome'), moa_new_name = 'Proteosome inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('HSP|shock'), moa_new_name = 'HSP inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('ubiq','Ubiq'), moa_new_name = 'E3 ubiquitin ligase inhibitor')

```

```{r HDAC inhibitors}
moas_prism_join <- str_annotate_1(str_vector = c('istone|HDAC'), moa_new_name = 'Histone deacetylase inhibitor')

```

```{r PAAAIN}
moas_prism_join <- str_annotate_1(str_vector = c('yclooxygenase'), moa_new_name = 'COX pathway inhibitor')
```


```{r Receptor inhibitor}
moas_prism_join <- str_annotate_1(str_vector = c('Vascular'), moa_new_name = 'VEGF receptor inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('erbB|pidermal|EGFR'), moa_new_name = 'EGF receptor inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('nsulin-like|nsulin |IGF'), moa_new_name = 'IGFR inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('derived|PDGF'), moa_new_name = 'PDGFR inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('FLT3|lt3'), moa_new_name = 'FLT3 receptor inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('Stem cell'), moa_new_name = 'SCGF receptor inhibitor')
```


```{r Corticoids receptor inhibitor}
moas_prism_join <- str_annotate_1(str_vector = c('lucocorticoid receptor agonist'), moa_new_name = 'Glucocorticoid receptor agonist')
moas_prism_join <- str_annotate_1(str_vector = c('lucocorticoid receptor antagonist'), moa_new_name = 'Glucocorticoid receptor antagonist')

moas_prism_join <- str_annotate_1(str_vector = c('romatase'), 
                                  moa_new_name = 'Aromatase inhibitor')


moas_prism_join <- str_annotate_1(str_vector = c('Mineralocorticoid'), 
                                  moa_new_name = 'Mineralocorticoid receptor antagonist')
```


```{r Dopamine recepetors}
moas_prism_join <- str_annotate_1(str_vector = c("dopa.*antagonist|Dopa.*antagonist"), 
                                  moa_new_name = 'Dopamine receptor antagonist')
moas_prism_join <- str_annotate_1(str_vector = c("dopa.*\\bagonist\\b|Dopa.*\\bagonist\\b"), 
                                  moa_new_name = 'Dopamine receptor partial agonist')
```


even if there are several types of adrenergic receptors or all grouped otherwise there are too low nº of drugs per group

```{r Adrenergic receptors}
#Add inhibitor
moas_prism_join <- str_annotate_1(str_vector = c("drenergic.*antagonist"), 
                                  moa_new_name = 'Adrenergic receptor antagonist')
moas_prism_join <- str_annotate_1(str_vector = c("drenergic.*\\bagonist\\b"), 
                                  moa_new_name = 'Adrenergic receptor agonist')

```

HISTAMINE IS NOT FINISHED YET

```{r Histamine receptor}

moas_prism_join <- str_annotate_1(str_vector = c("istamine.*antagonist"), 
                                  moa_new_name = 'Histamine receptor antagonist')
moas_prism_join <- str_annotate_1(str_vector = c("istamine.*\\bagonist\\b"), 
                                  moa_new_name = 'Histamine receptor agonist')

```

```{r Glutamate}

moas_prism_join <- str_annotate_1(str_vector = c('lutamate.*antagonist'), 
                                  moa_new_name = 'Glutamate receptor antagonist')
moas_prism_join <- str_annotate_1(str_vector = c('lutamate.*\\bagonist\\b',
                                                 'lutamate.*positive allosteric modulator'), 
                                  moa_new_name = 'Glutamate receptor agonist')
moas_prism_join <- str_annotate_1(str_vector = c('lutamate inhibitor',
                                                 'lutamate-gated'), 
                                  moa_new_name = 'Glutamate receptor modulator')
```


In bacteria, there are 2 type of DNa topoisomerases, and they are both put in the same group (Topoisomerase IV and bacterial DNA gyrase).

```{r DNA DRUGS}
## GDSC1
moas_prism_join <- str_annotate_1(str_vector = c('Topoisomerase IV','DNA gyrase'), 
                                  moa_new_name = 'Bacterial topoisomerase inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('DNA topoisomerase'), 
                                  moa_new_name = 'Topoisomerase inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('DNA.*ethyltransferase'), 
                                  moa_new_name = 'DNA methyltransferase inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('istone.*ethyltransferase'), 
                                  moa_new_name = 'Histone methylation regulator')

moas_prism_join <- str_annotate_1(str_vector = c('^DNA polymerase'), 
                                  moa_new_name = 'DNA polymerase inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('^DNA inhibitor'), 
                                  moa_new_name = 'DNA inhibitor')
```

the ribosome inhibitor contains both bacterial (70S, 50S) and eukaryote (80S)

```{r DNA not finished}

moas_prism_join <- str_annotate_1(str_vector = c('ribosome', 'Ribosome','ribosomal'), 
                                  moa_new_name = 'Ribosome inhibitor')


```

RNA polymerase contains both bacterial and viral

```{r RNA}

moas_prism_join <- str_annotate_1(str_vector = c('RNA polymerase','RNA replication'), 
                                  moa_new_name = 'RNA polymerase inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('RNA disrupting agent','RNA inhibitor'), 
                                  moa_new_name = 'RNA inhibitor')

```
RNA synthesis could be p.e. by DNa crosslinking which doesn't allow RNA synthesis
All serotonin are put togheter, both antagonist and agonsits, because not all are specified.

```{r Serotonin}
moas_prism_join <- str_annotate_1(str_vector = c('serotonin|Serotonin|HT'), 
                                  moa_new_name = 'Serotonin receptor regulator')
moas_prism_join <- str_annotate_1(str_vector = c("erotonin.*antagonist"), 
                                  moa_new_name = 'Serotonin receptor antagonist')
moas_prism_join <- str_annotate_1(str_vector = c("erotonin.*\\bagonist\\b"), 
                                  moa_new_name = 'Serotonin receptor agonist')

```

Thymidylate is abacterial enzyme.

```{r Thymidylate}
moas_prism_join <- str_annotate_1(str_vector = c('hymidylate'), 
                                  moa_new_name = 'Thymidylate synthase inhibitor')

```


```{r GSK3}
moas_prism_join <- str_annotate_1(str_vector = c('synthase kinase','GSK','lycogen'), 
                                  moa_new_name = 'GSK3 inhibitor')
```


```{r PKC inhibitor}
moas_prism_join <- str_annotate_1(str_vector = c('PKC'), 
                                  moa_new_name = 'PKC inhibitor')
```


Microtubule includes only tubulin and no actin actions.

```{r Tublin}
moas_prism_join %>% filter(grepl('tub|Tub',moas)) %>% arrange(moas)
```

```{r BCR ABL KINASE}
moas_prism_join <- str_annotate_1(str_vector = c('Bcr'), 
                                  moa_new_name = 'Bcr/Abl inhibitor')
```

```{r retinoid}
moas_prism_join <- str_annotate_1(str_vector = c('Retin|retin'), 
                                  moa_new_name = 'Retinoic acid receptor agonist')
```

The PPar inhibitors are annotated according tot he PRISM annotation, as it is incomplete in chembl. 

```{r lipid metabolism or receptors}

moas_prism_join <- str_annotate_1(str_vector = c('PPAR receptor agonist',
                                                 'Peroxisome proliferator-activated receptor.* agonist'), 
                                  moa_new_name = 'PPAR receptor agonist')


moas_prism_join <- str_annotate_1(str_vector = c('HMG'), 
                                  moa_new_name = 'HMG-CoA reductase inhibitor')

```

```{r Adenosine}

moas_prism_join <- str_annotate_1(str_vector = c('denosine.*\bagonist\b'), 
                                  moa_new_name = 'Adenosine receptor agonist')

moas_prism_join <- str_annotate_1(str_vector = c('denosine.*receptor.*antagonist'), 
                                  moa_new_name = 'Adenosine receptor antagonist')

```

```{r Cytoskeleton inhibitor}
moas_prism_join <- str_annotate_1(str_vector = c('Rho|rho'), moa_new_name = 'ROCK inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('elastase','Elastase'), 
                                  moa_new_name = 'Elastase inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('inesin'), 
                                  moa_new_name = 'Kinesin inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('Focal|focal'), 
                                  moa_new_name = 'Focal adhesion kinase inhibitor')
```

phospholipase ;phosphatase ;thymidine 

```{rH or TRH rceptor}

moas_prism_join <- str_annotate_1(str_vector = c('hosphofructokinase|exokinase'), 
                                  moa_new_name = 'Glycolysis kinase modulator')

moas_prism_join <- str_annotate_1(str_vector = c('monophosphatase'), 
                                  moa_new_name = 'Inositol monophosphatase inhibitor')


moas_prism_join <- str_annotate_1(str_vector = c('hyro'), 
                                  moa_new_name = 'TRH or TH recepor agonist')

```


```{r Growth factors receptor inhibitors}

moas_prism_join <- str_annotate_1(str_vector = c('^Insulin|^insulin'), 
                                  moa_new_name = 'IGF receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('ibroblast|FGF'), 
                                  moa_new_name = 'FGF receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('Vascular'), 
                                  moa_new_name = 'VEGF receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('erbB|pidermal|EGFR'), 
                                  moa_new_name = 'EGF receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('derived|PDGF'), 
                                  moa_new_name = 'PDGF receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('Stem cell'), 
                                  moa_new_name = 'SCGF receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('^Insulin|^insulin'), 
                                  moa_new_name = 'IGF receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('Met','MET','Hepatocyte growth factor'), 
                                  moa_new_name = 'HGF receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('acrophage'), 
                                  moa_new_name = 'MCSF receptor inhibitor')
```

The hepatocyte growth factor receptor is the protein coded by the c-met gene!

```{r Receptor inhibitor}

moas_prism_join <- str_annotate_1(str_vector = c('FLT3|lt3'), moa_new_name = 'FLT3 receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('Ephrin'), 
                                  moa_new_name = 'Ephrin receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('pioid'), 
                                  moa_new_name = 'Opidoid receptor regulator')


moas_prism_join <- str_annotate_1(str_vector = c('Endothelin','endothelin'), 
                                  moa_new_name = 'Endothelin receptor antagonist')

moas_prism_join <- str_annotate_1(str_vector = c('Trk','trk','TRK'), 
                                  moa_new_name = 'Nerve growth factor receptor Trk-A inhibitor')

```

```{r Cytochrome}

moas_prism_join <- str_annotate_1(str_vector = c('ytochrome P450'), 
                                  moa_new_name = 'Cytochrome P450 inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('C-C|hemokin|CXC'), 
                                  moa_new_name = 'CC-C chemokine receptor modulator')

moas_prism_join <- str_annotate_1(str_vector = c('anhydrase|arbonic'), 
                                  moa_new_name = 'Carbonic anhydrase inhibitor')


moas_prism_join <- str_annotate_1(str_vector = c('esterol'), 
                                  moa_new_name = 'Cholesterol ester transfer inhibitor')


moas_prism_join <- str_annotate_1(str_vector = c('Farnesyl','farnesyl'), 
                                  moa_new_name = 'Farnesyltransferase inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('eptidase'), 
                                  moa_new_name = 'Aminopeptidase inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('monophosphate'), 
                                  moa_new_name = 'IMPDH inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('romodomain|BET|BRD|extra-terminal'), 
                                  moa_new_name = 'Bromodomain inhibitor')


```


```{r NfkB pathway}
moas_prism_join <- str_annotate_1(str_vector = c('NFkB','nuclear factor kappa','NFkB'), 
                                  moa_new_name = 'NFkB pathway inhibitor')

```


```{r  tyr kianse}

moas_prism_join <- str_annotate_1(str_vector = c('RET'), 
                                  moa_new_name = 'RET tyrosine kinase inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('src|SRC|Src'), 
                                  moa_new_name = 'SRC tyrosine kinase inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('ALK |Alk |alk '), 
                                  moa_new_name = 'ALK tyrosine kinase inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('Abl |ABL | abl '), 
                                  moa_new_name = 'ABL tyrosine kinase inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('Bcr|BCR'), 
                                  moa_new_name = 'Bcr/Abl inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('Neurotrophic'), 
                                  moa_new_name = 'Neurotrophic tyrosine kinase receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('NT-3'), 
                                  moa_new_name = 'NT-3 growth factor receptor inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('TIE-2'), 
                                  moa_new_name = 'TIE-2 kinase inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('SYK'), 
                                  moa_new_name = 'SYK inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('HCK'), 
                                  moa_new_name = 'HCK inhibitor')
```



```{r Other kinases}
moas_prism_join <- str_annotate_1(str_vector = c('JAK','janus'), moa_new_name = 'JAK inhibitor') 
moas_prism_join <- str_annotate_1(str_vector = c('p38'), moa_new_name = 'p38 MAPK inhibitor')


moas_prism_join <- str_annotate_1(str_vector = c('Btk|btk|BTK'), moa_new_name = 'BTK inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('BRK|brk|Brk'), moa_new_name = 'BRK inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('FRK|Fyn|FYN'), moa_new_name = 'FRK inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('Lyn|LYN'), moa_new_name = 'Lyn inhibitor')
moas_prism_join <- str_annotate_1(str_vector = c('Lyn|LYN'), moa_new_name = 'Lyn inhibitor')
```


```{r Acetylcholin}
moas_prism_join <- str_annotate_1(str_vector = c('acetylcholin'), 
                                  moa_new_name = 'Acetylcholine receptor agonist')
```

```{r}
# moas_chembl_prism %>%  %>% group_by(mech_summary) %>% count() %>% arrange(desc(n))
#   filter(n >3) %>% filter(n <300) %>%arrange(desc(n)) %>% 
#   ggplot() + geom_bar(aes(x = mech_summary, y = n, fill = mech_summary), stat="identity" ) +
#   theme(legend.position="none",axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 4)) 
# moas_chembl_prism %>% group_by(moas)  %>% 
#   count() 
```

```{r Angiotensin}
moas_prism_join <- str_annotate_1(str_vector = c('ngiotensin'), 
                                  moa_new_name = 'Angiotensin antagonist')
```



OTX015 bromodomain

```{r  Sodium channels}
moas_prism_join <- str_annotate_1(str_vector = c('sodium channel blocker','Sodium channel.*blocker'), 
                                  moa_new_name = 'Sodium channel blocker')
```

Cotransporters are put togheer (bot cation/cation, cation/anion, and sodium/glucose)

```{r Potassium channels}
moas_prism_join <- str_annotate_1(str_vector = c('otassium channel.*opener','otassium channel.*activator'),
                                  moa_new_name = 'Sodium channel opener/activator')


moas_prism_join <- str_annotate_1(str_vector = c('otassium channel.*opener','otassium channel.*activator'),
                                  moa_new_name = 'Potassium channel blocker')
moas_prism_join <- str_annotate_1(str_vector =
                                    c('otassium.*transport','hloride*transport','odium.*transport'),
                                  moa_new_name = 'Potassium; Sodium or Chloride (co-)transporter inhibitor')


```



```{r  Calcium channels}
moas_prism_join <- str_annotate_1(str_vector = c('alcium channel.*blocker'), 
                                  moa_new_name = 'Calcium channel blocker')
moas_prism_join <- str_annotate_1(str_vector = c('alcium channel.*activator'), 
                                  moa_new_name = 'Calcium channel activator')

```

```{r PDE}
moas_prism_join <- str_annotate_1(str_vector = c('hosphodiesterase'),
                                  moa_new_name = 'Phosphodiesterase inhibitor')
```


```{r}
moas_prism_join <- str_annotate_1(str_vector = c('phosphoinositid'), 
                                  moa_new_name = '3-phosphoinositide dependent protein kinase-1 inhibitor')
```

```{r GABA}
moas_prism_join <- str_annotate_1(str_vector = c('GABA'), 
                                  moa_new_name = 'GABA modulator')
```


```{r TLR}
moas_prism_join <- str_annotate_1(str_vector = c('Toll','toll','TL'), 
                                  moa_new_name = 'TLR inhibitor')
```


```{r}
moas_prism_join <- str_annotate_1(str_vector = c('phosphoinositide'), 
                                  moa_new_name = '3-phosphoinositide dependent protein kinase-1 inhibitor')

```

```{r}
moas_prism_join <- str_annotate_1(str_vector = c('pim','PIM','Pim'), 
                                  moa_new_name = 'PIM kinase inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('syk','SYK'), 
                                  moa_new_name = 'SYK kinase inhibitor')

```

```{r}

moas_prism_join <- str_annotate_1(str_vector = c('aspase activator'), 
                                  moa_new_name = 'Caspase activator')

moas_prism_join <- str_annotate_1(str_vector = c('aspase.*inhibitor'), 
                                  moa_new_name = 'Caspase inhibitor')

```


```{r}
moas_prism_join <- str_annotate_1(str_vector = c('itric'), 
                                  moa_new_name = 'Nitric oxide inhibitor')
```


```{r}
moas_prism_join <- str_annotate_1(str_vector = c('orepinephrine'), 
                                  moa_new_name = 'Norepinephrine reuptake/transport inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('lycoprotein'), 
                                  moa_new_name = 'Glycoprotein inhibitor')


moas_prism_join <- str_annotate_1(str_vector = c('Ribonucleo.*reductase'), 
                                  moa_new_name = 'Ribonucleotide reductase inhibitor')
```


```{r}
moas_prism_join <- str_annotate_1(str_vector = c('Glycine receptor'), 
                                  moa_new_name = 'Glycine receptor agonist')


moas_prism_join <- str_annotate_1(str_vector = c('Glycine transporter|GlyT'), 
                                  moa_new_name = 'Glycine transporter inhibitor')

```

```{r DNA agent}

moas_prism_join <- str_annotate_1(str_vector = 
                                    c('alkyl','damage','DNA disrupting','cross','intercal','Choleretic'), 
                                  moa_new_name = 'DNA alkylating/crosslinking/intercalating agent')
```

```{r}
moas_prism_join <- str_annotate_1(str_vector = 
                                    c('opamine.*(transporter|uptake)'), 
                                  moa_new_name = 'Dopamine transporter/uptake inhibitor')
moas_prism_join %>% filter(grepl('metabolite',moas))
```

```{r}
moas_prism_join <- str_annotate_1(str_vector = c('Glucokinase','Pyruvate','Hexo','Phosphofructokinase'), 
                                  moa_new_name = 'Glycolysis kinase modulator')
```


```{r}
moas_prism_join %>% filter(grepl('PAK|p21',moas)) %>% arrange(moas_curated)

```

```{r}
moas_prism_join <- str_annotate_1(str_vector = c('Prostan.*\bagonist\b'), 
                                  moa_new_name = 'Prostanoid receptor agonist')
moas_prism_join <- str_annotate_1(str_vector = c('Prostan.*antagonist'), 
                                  moa_new_name = 'Prostanoid receptor antagonist')

moas_prism_join <- str_annotate_1(str_vector = c('edgehog|Smoo'), 
                                  moa_new_name = 'Hedgehog pathway inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('catenin|Wnt'), 
                                  moa_new_name = 'Wnt signaling inhibitor')

moas_prism_join <- str_annotate_1(str_vector = c('Iron'), 
                                  moa_new_name = 'Iron chelating agent')

moas_prism_join <- str_annotate_1(str_vector = c('casein','Casein'), 
                                  moa_new_name = 'Casein inhibitior')

moas_prism_join <- str_annotate_1(str_vector = c('Mitotic kinase','Monopol','Centrom'), 
                                  moa_new_name = 'Mitosis inhibitior')
```

MOAs annotation from PRISM
```{r}

moas_prism_join <- moas_prism_join %>% mutate(moas_curated = ifelse(moas_curated == '',moas,moas_curated))

write.csv(left_join(moas_prism_join %>% arrange(name,moas) %>% select(name,moas_curated) %>% distinct(),
          prism_data %>% select(name, target), by = 'name') %>% distinct() %>% arrange(moas_curated),
          file = 'figures/data/prism_curated_MOAs.csv')
```


Annotation of drugs in the NFkB pathway inhibitors has been mantained.

